Regime transition identification for basin's governance challenges of water use

### 2020-11-09 tex/main/manuscript.tex
update significance

% Please add a significance statement to explain the relevance of your work
% PNAS特有的“Significance陈述”，用不超过120个字来说明研究的意义和亮点
\significancestatement{
	% Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the significance statement is to explain the relevance of the work in broad context to a broad readership. The significance statement appears in the paper itself and is required for all research papers.
	Water, a key resource to support the sustainable development of human societies, whose natural cycle has been modified by growing socio-economic processes. We propose a new method with an integrated index to detect water utilization regimes and applying it to the Yellow River Basin, a typical overexploited basin in China. After sketching changes of relationships between social development and water utilization within the Yellow River Basin, we summarized a general transition framework. By predicting widespread development dilemmas, it can be a useful guideline for basins all around the world in their sustainable developing trajectories. 
}

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{ % 作者的相应贡献
	Shuai Wang and Bojie Fu designed this research,
	Shuang Song performed the research and analysed data,
	Shuang Song, Xutong Wu wrote the paper.
}
\authordeclaration{ % 利益冲突陈述
	The authors declare no competing interests.
}

>>>>

% Please add a significance statement to explain the relevance of your work
% PNAS特有的“Significance陈述”，用不超过120个字来说明研究的意义和亮点
\significancestatement{
\label{significance}
	% Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the significance statement is to explain the relevance of the work in broad context to a broad readership. The significance statement appears in the paper itself and is required for all research papers.
	It is a well-known fact that water use plays a key role in development of human societies.
	Therefore, as natural water cycle has been dominated by growing socio-economic processes, big river basins are roundly governed stage by stage for further water use. 
	We propose a new method with an integrated index to detect water governance regimes and applying it to the Yellow River Basin, a typical fast-changing basin in China.
	Since our index integrates various considerations of water governance (who gets what water, when and how), a widespread regime transition schema can be summarized after then. 
	By identifying governance challenges, the schema can be a useful guideline for basins all around the world in their sustainable developing trajectories. 
}

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{ % 作者的相应贡献
	Shuai Wang and Bojie Fu designed this research,
	Shuang Song performed the research and analysed data,
	Shuang Song, Xutong Wu wrote the paper.
	Yongping Wei reviewed the manuscript and proposed major useful advices.
}
\authordeclaration{ % 利益冲突陈述
	The authors declare no competing interests.
}
